final figures for inclusion

### 2021-04-14 shared analysis files /data_wrangling_plot.Rmd
rethinking contour plot

```{r, echo= FALSE, message= FALSE}
#GAM APPROACH
#fit GAM
gam1<-gam(yi~te(mean_temp_constant,flux_range,k=7),data=normalized) # note, lots of decisions that I blew by here
summary(gam1)
#estimate values via gam
vals<-expand.grid(flux_range=seq(0,20,length.out = 100), mean_temp_constant=seq(0,35,length.out = 100))
pd.gam<-predict(gam1,newdata=vals)
surf<-data.frame(vals,value=pd.gam)
vertices <- data.frame(
  x = c(0, 0, 20),
  y = c(10, 0, 0), 
  id = c("a", "a", "a")
)
#plot values as a surface
```

```{r, echo= FALSE, message= FALSE}
#plot gam surface
ggplot()+
  geom_raster(data = surf, aes(x=mean_temp_constant,y=flux_range, fill=value))+
  geom_contour(data = surf, 
               aes(x=mean_temp_constant,y=flux_range,z=value), colour=gray(0.2),binwidth=0.5,size=0.2)+
  geom_contour(data = surf,  aes(x=mean_temp_constant,y=flux_range,z=value), 
               colour="black", breaks=c(0),size=2)+
  #geom_contour_filled()
  scale_x_continuous('Mean Temp (°C)',expand=c(0,0))+
  scale_y_continuous('Temp Range (°C)',expand=c(0,0))+
  scale_fill_gradientn('Effect Size',
                       colors= viridis(100),
                       breaks=seq(-2,5,2),limits=c(-2,5),
                       guide = guide_colourbar(ticks.colour = gray(.2),
                                               ticks.linewidth = 1.,
                                               frame.colour = "black"))+
  coord_cartesian(xlim=c(0,35),ylim=c(0,20))+
  geom_jitter(data = normalized, mapping = aes(x=mean_temp_constant,y=flux_range,z= yi,fill = yi),
              alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Effect Size', limits = c(-2,5), option = "C")+
  theme_bw()+ 
  theme(legend.position="bottom")+
  geom_polygon(data = vertices, mapping = aes(x = x, y = y), fill = "gray")
```
**Figure 3.** Contour plot of GAM generated effects sizes overlayed with raw effect sizes from the extracted dataset. Black lines denote the boundary from negative to positive effect sizes. Grey triange denotes excluded contour that lacks any raw data.

@@

- How do all the different models sound? Does it make sense to have these different models?
- Do the figures match up with the story/questions associated with them?
- Jittering versus standard plotting for the regression plots?
_________________________________
Supplementary Plots/Code

>>>>

```{r, echo= FALSE, message= FALSE}
#GAM APPROACH
#fit GAM
gam1<-gam(yi~te(mean_temp_constant + te(as.factor(flux_range), k=7)),data=normalized) # note, lots of decisions that I blew by here
summary(gam1)
#estimate values via gam
vals<-expand.grid(flux_range=seq(0,20,length.out = 100), mean_temp_constant=seq(0,35,length.out = 100))
pd.gam<-predict(gam1,newdata=vals)
surf<-data.frame(vals,value=pd.gam)
vertices <- data.frame(
  x = c(0, 0, 20),
  y = c(10, 0, 0), 
  id = c("a", "a", "a")
)
#plot values as a surface
```

```{r, echo= FALSE, message= FALSE}
#plot gam surface
ggplot()+
  geom_raster(data = surf, aes(x=mean_temp_constant,y=flux_range))+
  geom_contour(data = surf, 
               aes(x=mean_temp_constant,y=flux_range,z=value), colour=gray(0.2),binwidth=0.5,size=0.2)+
  geom_contour(data = surf,  aes(x=mean_temp_constant,y=flux_range,z=value), 
               colour="black", breaks=c(0),size=2)+
  #geom_contour_filled()
  scale_x_continuous('Mean Temp (°C)',expand=c(0,0))+
  scale_y_continuous('Temp Range (°C)',expand=c(0,0))+
  scale_fill_gradientn('Effect Size',
                       colors= viridis(100),
                       breaks=seq(-2,5,2),limits=c(-2,5),
                       guide = guide_colourbar(ticks.colour = gray(.2),
                                               ticks.linewidth = 1.,
                                               frame.colour = "black"))+
  coord_cartesian(xlim=c(0,35),ylim=c(0,20))+
  geom_jitter(data = normalized, mapping = aes(x=mean_temp_constant,y=flux_range,z= yi,fill = yi),
              alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Effect Size', limits = c(-2,5), option = "C")+
  theme_classic()+ 
  theme(legend.position="bottom")+
  geom_polygon(data = vertices, mapping = aes(x = x, y = y), fill = "gray")

normalized %>%
ggplot(aes(x=mean_temp_constant, y=flux_range, fill = yi))+
  geom_jitter(data = normalized, mapping = aes(x=mean_temp_constant,y=flux_range,z= yi,fill = yi),
              alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Effect Size', limits = c(-2,5), option = "C")
```
**Figure 3.** Contour plot of GAM generated effects sizes overlayed with raw effect sizes from the extracted dataset. Black lines denote the boundary from negative to positive effect sizes. Grey triange denotes excluded contour that lacks any raw data.

@@

- How do all the different models sound? Does it make sense to have these different models?
- Do the figures match up with the story/questions associated with them?
- Jittering versus standard plotting for the regression plots?

```{r}
normalized %>%
  ggplot(aes(y=yi, x=mean_temp_constant, color = flux_range))+
  geom_point(size=4)+
  scale_color_viridis(option= "B")+
  theme_classic()

normalized %>%
  ggplot(aes(y=flux_range, x=mean_temp_constant, color = yi))+
  geom_jitter(size=4)+
  scale_color_viridis(option= "B")+
  theme_classic()

_________________________________
Supplementary Plots/Code
